A matrix-free approach for finite-strain hyperelastic problems using geometric multigrid

### 2019-02-06 doc/large_strain.tex
remove todo and white spaces

As outlined in the introduction, it is not only the performance of the matrix-free vector multiplication, but also the memory requirement to store a sparse matrix which is the driving force behind matrix-free methods.
Figures \ref{fig:benchmark_miehe_Emmy_memory2}, \ref{fig:benchmark_miehe_Emmy_memory3}, \ref{fig:benchmark_miehe_IWR_memory2} and \ref{fig:benchmark_miehe_IWR_memory3} demonstrate that even with caching one fourth-order symmetric tensor and one second-order tensor at each quadrature point \changeJP{(``tensor4'')}, the matrix-free approach takes much less memory than its matrix-based counterpart.
{\color{red}
In those graphs we report the \changeJP{overall} memory needed to cache additional quantities required for the tangent operator here considered,
as well as the memory required by the \texttt{deal.II} \textit{MatrixFree} object, which caches the inverse of the Jacobian of the transformation
from unit to real cell \cite{kronbichler12}.
Note that for Algorithm \ref{alg:mf_scalar} we need to evaluate gradients with respect to both \changeJP{deformed} and undeformed
configurations, and therefore two inverses will be cached via two different \textit{MatrixFree} objects.\todo{this is roughly main memory transfer, do we elaborate on this/use it? I don't think so}}

>>>>

As outlined in the introduction, it is not only the performance of the matrix-free vector multiplication, but also the memory requirement to store a sparse matrix which is the driving force behind matrix-free methods.
Figures \ref{fig:benchmark_miehe_Emmy_memory2}, \ref{fig:benchmark_miehe_Emmy_memory3}, \ref{fig:benchmark_miehe_IWR_memory2} and \ref{fig:benchmark_miehe_IWR_memory3} demonstrate that even with caching one fourth-order symmetric tensor and one second-order tensor at each quadrature point \changeJP{(``tensor4'')}, the matrix-free approach takes much less memory than its matrix-based counterpart.
{\color{red}
In those graphs we report the \changeJP{overall} memory needed to cache additional quantities required for the tangent operator here considered,
as well as the memory required by the \texttt{deal.II} \textit{MatrixFree} object, which caches the inverse of the Jacobian of the transformation
from unit to real cell \cite{kronbichler12}.
Note that for Algorithm \ref{alg:mf_scalar} we need to evaluate gradients with respect to both \changeJP{deformed} and undeformed
configurations, and therefore two inverses will be cached via two different \textit{MatrixFree} objects.}
